Supporting Information for ``Seniority and hierarchy configuration interaction for radicals and excited states''

### 2023-08-28 Manuscript/Cover_Letter/Cover_Letter.tex
response letter

We suggest Paul Johnson, Gianluca Levi, Hannes Jonsson, Stijn de Baerdemacker, Eric Neuscamman, Katharina Boguslawski, and Peter Knowles as potential referees.
We look forward to hearing from you soon.

>>>>

We suggest Paul Johnson, Gianluca Levi, Hannes Jonsson, Stijn de Baerdemacker, Eric Neuscamman, and Katharina Boguslawski as potential referees.
We look forward to hearing from you soon.
